Supplement

### 2023-04-11 06_Paper/ER-ED/ERED_Stage2/Supplement.Rmd
created supplement

---
title: "Supplement"
author: "Christoph Scheffel"
date: "2023-02-16"
output: html_document
---

```{r SetupSupplement, include = FALSE}
knitr::opts_chunk$set(echo = FALSE)

@@

# Supplementary Material {#SupplementaryMaterial}

\includepdf[pages={-}, landscape=true]{Supplement/StimList_Suppl.pdf}
\counterwithin{figure}{section}
\counterwithin{table}{section}
\setcounter{section}{19}
\setcounter{figure}{0}
\setcounter{table}{1}
\newpage

>>>>

---
title             : "Supplementary Material for the Registered Report: Estimating individual subjective values of emotion regulation strategies"
shorttitle        : "Supplementary Material"
author:
  - name          : "Christoph Scheffel"
    orcid         : "0000-0001-5963-9229"
    affiliation   : "1"
    corresponding : yes
    address       : "Zellescher Weg 17, 01069 Dresden, Germany"
    email         : "christoph_scheffel@tu-dresden.de"
    equal_contrib : yes
    role          :         # Contributorship roles (e.g., CRediT, https://casrai.org/credit/)
      - Conceptualization
      - Methodology
      - Funding acquisition
      - Formal analysis
      - Investigation
      - Project administration
      - Software
      - Visualization
      - Writing - original draft preparation
      - Writing - review & editing
  - name          : "Josephine Zerna"
    orcid         : "0000-0003-2892-884X"
    affiliation   : "1"
    equal_contrib : yes
    role          :
      - Conceptualization
      - Methodology
      - Funding acquisition
      - Investigation
      - Project administration
      - Software
      - Visualization
      - Writing - review & editing
  - name          : "Anne Gärtner"
    orcid         : "0000-0003-4296-963X"
    affiliation   : "1"
    role          :
      - Formal analysis
      - Writing - review & editing
  - name          : "Denise Dörfel"
    orcid         : "0000-0002-5632-419X"
    affiliation   : "1,2"
    role          :
      - Conceptualization
      - Writing - review & editing
  - name          : "Alexander Strobel"
    orcid         : "0000-0002-9426-5397"
    affiliation   : "1"
    role          :
      - Conceptualization
      - Methodology
      - Writing - review & editing 
affiliation       :
  - id            : "1"
    institution   : "Chair of Differential and Personality Psychology, Faculty of Psychology, Technische Universität Dresden, 01069 Dresden, Germany"
  - id            : "2"
    institution   : "Center for Information Services and High Performance Computing, Technische Universität Dresden, 01069 Dresden, Germany"
authornote        :
keywords          : "emotion regulation, regulatory effort, effort discounting, registered report, emotion regulation choice, emotion regulation flexibility, electromyography"
wordcount         : "9432"
bibliography      : ["ER_ED.bib"]
floatsintext      : yes
figsintext        : yes
figurelist        : no
tablelist         : no
footnotelist      : no
linenumbers       : yes
mask              : no
draft             : no
documentclass     : "apa6"
classoption       : "man"
output            : papaja::apa6_pdf
csl               : nature.csl
header-includes   :
    - \usepackage{booktabs}
    - \usepackage{longtable}
    - \usepackage{array}
    - \usepackage{multirow}
    - \usepackage{wrapfig}
    - \usepackage{float}
    - \usepackage{colortbl}
    - \usepackage{pdflscape}
    - \usepackage{tabu}
    - \usepackage{threeparttable}
    - \usepackage{threeparttablex}
    - \usepackage[normalem]{ulem}
    - \usepackage{makecell}
    - \usepackage{xcolor}
    - \usepackage{setspace}\doublespacing
    - \usepackage[final]{pdfpages}
    - \usepackage{chngcntr}
---

```{r SetupSupplement, include = FALSE}
knitr::opts_chunk$set(echo = FALSE)
knitr::opts_chunk$set(out.width = "\\textwidth")

@@

## Design Table {#DesignTable}

\includepdf[pages={-}, landscape=true]{Supplement/Design_Table_T2.pdf}
\newpage

## Stimuli used in ER paradigm

\includepdf[pages={-}, landscape=true]{Supplement/StimList_Suppl.pdf}

\renewcommand\thesection{\Alph{section}}
\counterwithin{figure}{section}
\counterwithin{table}{section}
\setcounter{section}{19}
\setcounter{figure}{0}
\setcounter{table}{1}
\newpage
